### 2018-02-24 DASFAA18_CR/Gruba_final/02-overview.tex

\begin{definition}
\label{def:blog}
A microblog $M_b = (O, T, M, flag)$ has its owner $O$ (a.k.a. user in this paper) to whom $M_b$ belongs (either \twd{} or \retd{}), the generated time $T$ of $M_b$, the message context $M$, and $flag$ denoting $M_b$ is \retd{} or originally tweeted by $O$. Here we use 1 and 0 to denote \retd{} and  tweeted, respectively.
\end{definition}

@@

\begin{figure}[tb!]
\centering
\includegraphics[width=.5\linewidth]{figures/architecture.eps}
\vspace{-1ex}
\caption{\sys{} Architecture}
\label{fig:framework}
\vspace{-4ex}
\end{figure}

>>>>

\begin{definition}
\label{def:blog}
A microblog $M_b = (O, T, M, flag)$ has its owner $O$ (a.k.a. user in this paper) to whom $M_b$ belongs (either \twd{} or \retd{}), the generated time $T$ of $M_b$, the message context $M$, and $flag$ denoting $M_b$ is \retd{} or originally \tw{} by $O$. Here we use 1 and 0 to denote \retd{} and  \tw{}, respectively.
\end{definition}

@@

\begin{figure}[tb!]
\centering
\includegraphics[width=.7\linewidth]{figures/architecture.eps}
\vspace{-1ex}
\caption{\sys{} Architecture}
\label{fig:framework}
\vspace{-4ex}
\end{figure}

### 2018-02-24 DASFAA18_CR/Gruba_final/04-uc.tex

\par Providing the \textit{Feature Data}, the User Clustering module takes the charge of grouping each user concerned into a proper cluster,
as illustrated in  Algorithm \ref{alg:uc}.
%
The idea is to enumerate a number of clustering trials (line \ref{enu}) and select the optimal solution with the best Silhouette coefficient value ($v$ in line \ref{opti}).
In principle, each trial (referred by $t$ in line \ref{enu}) first performs a clustering task (line \ref{task}; to be detailed in section \ref{sec:cluster}), resulting a cluster (by $l(u)$) for each user $u$ (line \ref{l});
then, each user obtains a Silhouette coefficient value $v(u)$ stemmed from the in/out-cluster distances (lines \ref{v-b}--\ref{v-e}; shall be illustrated in section \ref{sec:compu});
finally, the averaged Silhouette coefficient value of all users serves as the Silhouette coefficient value of the current trial, written as $v(t)$ (line \ref{avg}), by which the said selection process is conducted (line \ref{opti}).

\begin{algorithm}[t]
\begin{small}
\caption{User Clustering in \sys{}}
\label{alg:uc}
\begin{algorithmic}[1]
\State Input: \textit{Feature Data} $F$  of a set of users, the minimum/maximum number of clusters $N_i$ and $N_a$
\State Output: Optimal user clustering result $R$
\vspace{1ex}
\ForAll {$t \in [N_i, N_a]$} \label{enu}
	%\State group users into $t$ clusters by $F$; 
    \State perform K-Gru over F to get t clusters \label{task}
	\State clustering result $R'(t)\ =\ \{(u,\ l(u))\}$ with cluster info $l(u)$ for each user $u$; \label{l}
	\ForAll {$u \in \{u\}$}
		\State in-cluster distance $d_i(u)$ \label{v-b};
		\State out-cluster distance $d_o(u)$;
		\State Silhouette coefficient value $v(u)\ :=\ \frac{(d_o - d_i)}{max(d_o,\ d_i)}$; \label{v-e}
	\EndFor
	\State $v(t)\ :=\ Avg\{v(u)\}$; \label{avg}
\EndFor
\If {$v(a)\ =\ \ Max\{v(t)\}$} \label{opti}
	\State $R$ := $R'(a)$;
\EndIf
\State \bfseries{return} $R$.
\end{algorithmic}
\end{small}
\end{algorithm}

@@

As aforementioned, the clustering of K-Gru rests on the distance between vector samples, where the dimensions are combined with numbers (normalized to 0-1 range), categories and normalized vectors. For simplicity, we shall first illustrate the distance calculation of the simple vectors with a single data type on each dimension, and then demonstrate that of complex vectors.

@@

For categorical vectors $Y''\ = (y''_0, y''_1, \ldots)$ and  $Z''\ = (z''_0, z''_1, \ldots)$, the \hd{} \cite{IEEEexample:huang1997clustering} of $Y''$ and $Z''$ is:
%
\begin{equation}
\label{eq:hd}
D_h(Y'', Z'') = \sum_{\substack{e}} H_e,
\end{equation}
where $H_e$ refers to the \hd{} over each dimension, with $H_e = 1$ if $y''_e$ and $z''_e$ share the identical value, and $H_e = 0$, otherwise.

Regarding two vectors where each dimension is a normalized vector per se, Cosine Similarity is leveraged to compute the distance.
Then, the distance between such two vectors $Y^{\ast}\ = (Y^{\ast}_0, Y^{\ast}_1, ...)$ and $Z^{\ast}\ = (Z^{\ast}_0, Z^{\ast}_1, ...)$ is:
%
\begin{equation}
\label{eq:vd}
D_v(Y^{\ast}, Z^{\ast}) = 1- \sum_{\substack{e}} Y^{\ast}_e \cdot Z^{\ast}_e,
\end{equation}
where $\cdot$ refers to the dot product operation between two normalized vectors $Y^{\ast}_e$ and $Z^{\ast}_e$.

@@

\begin{table}[tb!]
\centering
\begin{small}
%\caption{Types of Dimensional Data in \textit{Feature Data} Vector}
\caption{Dimension Types in \textit{Feature Data} Vector}
%\vspace{0.1cm}
\label{tbl:data-type}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{l}{\textbf{Types}} & \multicolumn{1}{l}{\textbf{Data Dimensions}}	\\	\midrule \midrule
numerical data				& $\#R_u$, $\#E_u$, $R_{ee,u}$, $\#B_u$, $R_{oc,u}$, $\#W_{r,u}$,$\#W_{t,u}$               \\	\midrule 				
categorical data			& $G_u, P_u, U_{t,u}$				\\	\midrule
normalized vectors			& $P_{rt,u}$, $P_{rg,u}$, $P_{tt,u}$, $P_{tg,u}$, $P_u$			\\ \bottomrule
\end{tabular}
\end{small}
\end{table}

>>>>

\par Providing the \textit{Feature Data}, the User Clustering module takes the charge of grouping each user concerned into a proper cluster,
as illustrated in  Algorithm \ref{alg:uc}.
%
The idea is to enumerate a number of clustering trials (line \ref{enu}) and select the optimal solution with the best Silhouette coefficient value ($v$ in line \ref{opti}).
In principle, each trial (referred by $t$ in line \ref{enu}) first performs a clustering task (line \ref{task} to be detailed in section \ref{sec:cluster}), resulting a cluster (by $l(u)$) for each user $u$ (line \ref{l});
then, each user obtains a Silhouette coefficient value $v(u)$ stemmed from the in/out-cluster distances (lines \ref{v-b}--\ref{v-e}; shall be illustrated in section \ref{sec:compu});
finally, the averaged Silhouette coefficient value of all users serves as the Silhouette coefficient value of the current trial, written as $v(t)$ (line \ref{avg}), by which the said selection process is conducted (line \ref{opti}).

\begin{algorithm}[t]
\begin{small}
\caption{User Clustering in \sys{}}
\label{alg:uc}
\begin{algorithmic}[1]
\State Input: \textit{Feature Data} $F$  of a set of users, the minimum/maximum number of clusters $N_i$ and $N_a$
\State Output: Optimal user clustering result $R$
\vspace{1ex}
\ForAll {$t \in [N_i, N_a]$} \label{enu}
	%\State group users into $t$ clusters by $F$; \label{task}
    \State perform K-Gru over F to get t clusters
	\State clustering result $R'(t)\ =\ \{(u,\ l(u))\}$ with cluster info $l(u)$ for each user $u$; \label{l}
	\ForAll {$u \in \{u\}$}
		\State in-cluster distance $d_i(u)$ \label{v-b};
		\State out-cluster distance $d_o(u)$;
		\State Silhouette coefficient value $v(u)\ :=\ \frac{(d_o - d_i)}{max(d_o,\ d_i)}$; \label{v-e}
	\EndFor
	\State $v(t)\ :=\ Avg\{v(u)\}$; \label{avg}
\EndFor
\If {$v(a)\ =\ \ Max\{v(t)\}$} \label{opti}
	\State $R$ := $R'(a)$;
\EndIf
\State \bfseries{return} $R$.
\end{algorithmic}
\end{small}
\end{algorithm}

@@

\begin{table}[tb!]
\centering
\begin{small}
%\caption{Types of Dimensional Data in \textit{Feature Data} Vector}
\caption{Dimension Types in \textit{Feature Data} Vector}
\vspace{0.1cm}
\label{tbl:data-type}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{l}{\textbf{Types}} & \multicolumn{1}{l}{\textbf{Data Dimensions}}	\\	\midrule \midrule
numerical data				& $\#R_u$, $\#E_u$, $R_{ee,u}$, $\#B_u$, $R_{oc,u}$, $\#W_{r,u}$,$\#W_{t,u}$               \\	\midrule 				
categorical data			& $G_u, P_u, U_{t,u}$				\\	\midrule
normalized vectors			& $P_{rt,u}$, $P_{rg,u}$, $P_{tt,u}$, $P_{tg,u}$, $P_u$			\\ \bottomrule
\end{tabular}
\end{small}
\end{table}

As aforementioned, the clustering of K-Gru rests on the distance between vector samples, where the dimensions are combined with numbers (normalized to 0-1 range), categories and normalized vectors. For simplicity, we shall first illustrate the distance calculation of the simple vectors with a mono data type on each dimension, and then demonstrate that of complex vectors.

@@

For categorical vectors $Y''\ = (y''_0, y''_1, \ldots)$ and  $Z''\ = (z''_0, z''_1, \ldots)$, the \hd{} \cite{IEEEexample:huang1997clustering} of $Y''$ and $Z''$ is:
%
\begin{equation}
\label{eq:hd}
D_h(Y'', Z'') = \sum_{\substack{e}} H_e,
\end{equation}
where $H_e$ refers to the \hd{} over each dimension, with $H_e = 0$ if $y''_e$ and $z''_e$ share the identical value, and $H_e = 1$, otherwise.

Regarding two vectors where each dimension is a normalized vector per se, Cosine Similarity is leveraged to compute the distance.
Then, the distance between such two vectors $Y^{\ast}\ = (Y^{\ast}_0, Y^{\ast}_1, ...)$ and $Z^{\ast}\ = (Z^{\ast}_0, Z^{\ast}_1, ...)$ is:
%
\begin{equation}
\label{eq:vd}
D_v(Y^{\ast}, Z^{\ast}) = 1- Y^{\ast}_e \cdot Z^{\ast}_e,
\end{equation}
where $\cdot$ refers to the dot product operation between two normalized vectors $Y^{\ast}_e$ and $Z^{\ast}_e$.

@@

### 2018-02-24 DASFAA18_CR/Gruba_final/05-gm.tex

	\stab(1) \stitle{User Info} contains a list of aforementioned metrics \{$G_u$, $P_u$, \#$R_u$, \#$E_u$, $R_{ee,u}$\}.

@@

The modeling of retweeting behavior of groups is treated as a classification problem, and utilize the random forest classifier to address it. Details for random forest \cite{IEEEexample:conf/icdar/Ho1995} are omitted here for space reason.
The advantage of this classification model lies in that it could integrate different features conveniently, and
%The advantage of using classification model is that we can integrate different combinations of the features into the model conveniently.
the obtained group behavior model could learn what a positive/negative item looks like over each metric mentioned above.

Here we use accuracy to evaluate our model. To define accuracy, we set four variables: $E_{tp}$,$E_{fp}$,$E_{tn}$ and $E_{fn}$. For a given item $E$, if $E$ is a positive item and our model also determines it a positive item, then we set $E_{tp}$ to 1, else we set $E_{tp}$ to 0. If $E$ is a negative item and our model determines it a positive item, then we set $E_{fp}$ to 1, else we set $E_{fp}$ to 0. If $E$ is a negative item and our model determines it a negative item, then we set $E_{tn}$ to 1, else we set $E_{tn}$ to 0. If $E$ is a positive item and our model determines it a negative item, then we set $E_{fn}$ to 1, else we set $E_{fn}$ to 0.  Formally, accuracy is defined as:

\begin{equation}
\label{eq:def-presision}
accuracy = \frac{\sum_{\substack{E}} (E_{tp} + E_{tn} )}{ \sum_{\substack{E}} (E_{tp} + E_{tn} + E_{fp} + E_{fn}) }.
\end{equation}

>>>>

	\stab(1) \stitle{User Info} contains a list of aforementioned metrics \{$G_u$, $P_u$,\#$R_u$, \#$E_u$, $R_{ee,u}$\}.

@@

The modeling of retweeting behavior of groups is treated as a classification problem, and utilize the random forest classifier to address it. Details for random forest \cite{IEEEexample:conf/icdar/Ho1995} are omitted here for space reason.
The advantage of this classification model lies in that it could integrate different features conveniently, and
%The advantage of using classification model is that we can integrate different combinations of the features into the model conveniently.
the obtained group behavior model could learn what a positive/negative item looks like over each metric mentioned above. \par
Here we use accuracy to evaluate our model. To define accuracy, we set four variables: $E_{tp}$,$E_{fp}$,$E_{tn}$ and $E_{fn}$. For a given item $E$, if $E$ is a positive item and our model also determines it a positive item, then we set $E_{tp}$ to 1, else we set $E_{tp}$ to 0. If $E$ is a negative item and our model determines it a positive item, then we set $E_{fp}$ to 1, else we set $E_{fp}$ to 0. If $E$ is a negative item and our model determines it a negative item, then we set $E_{tn}$ to 1, else we set $E_{tn}$ to 0. If $E$ is a positive item and our model determines it a negative item, then we set $E_{fn}$ to 1, else we set $E_{fn}$ to 0. So the accuracy can be defined as:

\begin{equation}
\label{eq:def-presision}
accuracy = \frac{\sum_{\substack{E}} (E_{tp} + E_{tn} )}{ \sum_{\substack{E}} (E_{tp} + E_{tn} + E_{fp} + E_{fn}) }
\end{equation}

We use accuracy to test results of using various $\alpha$ values. Suppose the label set we manually labeled for each microblog is $A$, the label set our method labeled is $B$.
The accuracy can be defined as:
\begin{equation}
\label{eq:def-accuracy}
accuracy = \frac{ A \cap B }{ A \cup B }
\end{equation}

To define accuracy, we set four variables: $E_{tp}$,$E_{fp}$,$E_{tn}$ and $E_{fn}$. For a given item $E$, if $E$ is a positive item and our model also determines it a positive item, then we set $E_{tp}$ to 1, else we set $E_{tp}$ to 0. If $E$ is a negative item and our model determines it a positive item, then we set $E_{fp}$ to 1, else we set $E_{fp}$ to 0. If $E$ is a negative item and our model determines it a negative item, then we set $E_{tn}$ to 1, else we set $E_{tn}$ to 0. If $E$ is a positive item and our model determines it a negative item, then we set $E_{fn}$ to 1, else we set $E_{fn}$ to 0. So the accuracy can be defined as:

\begin{equation}
\label{eq:def-presision}
accuracy = \frac{\sum_{\substack{E}} (E_{tp} + E_{tn} )}{ \sum_{\substack{E}} (E_{tp} + E_{tn} + E_{fp} + E_{fn}) }
\end{equation}

### 2018-02-24 DASFAA18_CR/Gruba_final/06-perf.tex

\stitle{Exp-1: Interest Extraction}
%
Fig.\ \ref{fig:fe} shows the testing results of using various $\alpha$ values.
We report the interest accuracy with various $\alpha$ values. Suppose that the label set manually labeled for each microblog is $A$, the label set that our method labeled is $B$. The interest accuracy is defined as $\frac{ A \cap B }{ A \cup B }$.

System \sys{} reaches the optimal results when $\alpha$ is 0.7,
upon which the interest feature extracting is performed for the overall dataset with 43.5K users and 24 million microblogs.
In general, it performs well when $\alpha$ falls into $[0, 0.8]$.

@@

%\begin{figure}[tb!]
%  \centering
%  \subfigure[Tests with Various $\alpha$.]{
%    \label{fig:fe}
%\includegraphics[width=.355\linewidth]{figures/Interests}}
%  \hspace{0.5in}
%   \subfigure[Silhouette Coefficient Tests.]{
%    \label{fig:10-c}
%  \includegraphics[width=.355\linewidth]{figures/clustering}}
%  \caption{Performance of \sys{} Versus LRC-BQ.}
%    \label{fig:fig-1}
%\end{figure}

\begin{figure}[tb!]
\centering
\begin{minipage}{.5\textwidth}
  \centering
\includegraphics[width=.85\linewidth]{figures/Interests}
\caption{Interest Extraction: Varying $\alpha$.}
\label{fig:fe}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
\includegraphics[width=.8\linewidth]{figures/clustering}
\caption{Silhouette Coefficient Tests.}
\label{fig:10-c} 
\end{minipage}
\end{figure}

\begin{figure*}[tb!]
%\centering
  \subfigure[\sys{} Vs. LRC-BQ]{
    \label{fig:10-a}
    %\vspace{2ex}
    \includegraphics[width=0.5\textwidth]{figures/precision-1.eps}}
 % \hspace{0.5in}
   \subfigure[Varying Items]{
   %\vspace{2ex}
    \label{fig:11-a}
  \includegraphics[width=0.5\textwidth]{figures/precisionofdifferentfeatures.eps}}
  %\vspace{-1ex}
  \caption{Accuracy Evaluation.}
  \label{fig:fig-2}
  \vspace{-4ex}
\end{figure*}

@@

Fig.\ \ref{fig:11-a} explores the performance of \sys{} when using alternative data items for modeling.
By default, \sys{} uses ``UI+II+MI'', i.e., items of users (UI), microblogs (MI) and interactions (II).
%How about using other combinations of the above item(s)?
As shown in Fig.\ \ref{fig:11-a}, the default setting wins in most cases.

@@

\begin{figure*}[tb!]
\vspace{-2ex}
  \centering
  \subfigure[]{
      \label{fig:userFeatures:uf-1}
      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/1.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-2}
      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/2.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-3}
      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/3.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-4}
      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/4.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-5}
      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/5.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-6}
      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/6.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-7}
      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/7.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-8}
      \includegraphics[width=0.36\textwidth]{IMAGE/features/userFeatures/8.eps}}
  \caption{Visualization for User Features.}
  \label{fig:userFeatures} %% label for entire figure
  \vspace{-4ex}
\end{figure*}

@@

%\noindent\textbf{Summary}. %From these experimental results we find the followings.
%(1) We design a novel method to extract users' explicit/implicit interests, and case studies show that our method is effective.
%(2) In this paper, we offer a clustering method K-Gru to deal with complex vectors. And it helps us find a reasonable clustering result.
%
To conclude, by modeling user behaviors over groups instead of a single model for all users such as LRC-BQ, we improve the average accuracy over LRC-BQ by 6\%. What deserves to be mentioned is that the performance of LRC-BQ is also improved significantly by user clustering.

>>>>

\stitle{Exp-1: Feature Extraction}
%
Fig.\ \ref{fig:fe} shows the testing results of using various $\alpha$ values.
System \sys{} reaches the optimal results when $\alpha$ is 0.7,
upon which the interest feature extracting is performed for the overall dataset with 43.5K users and 24 million microblogs.
In general, it performs well when $\alpha$ falls into $[0, 0.8]$.

@@

\begin{figure*}[tb!]
  \centering
  \subfigure[Tests with Various $\alpha$.]{
    \label{fig:fe}
\includegraphics[width=.355\linewidth]{figures/Interests}}
  \hspace{0.5in}
   \subfigure[Silhouette Coefficient Tests.]{
    \label{fig:10-c}
  \includegraphics[width=.355\linewidth]{figures/clustering}}
%  \caption{Performance of \sys{} Versus LRC-BQ.}
    \label{fig:fig-1}
    \vspace{-4ex}
\end{figure*}

%\begin{figure}[tb!]
%\centering
%\includegraphics[width=.315\linewidth]{figures/Interests}
%\caption{Testing Results with Various $\alpha$.}
%\label{fig:fe}
%\vspace{-4ex}
%\end{figure}

%\begin{figure}[tb!]
%\centering
%\includegraphics[width=.315\linewidth]{figures/clustering}
%\caption{Silhouette Coefficient Tests.}
%\label{fig:uc}
%\vspace{-5ex}
%\end{figure}

\begin{figure*}[tb!]
\centering
  \subfigure[Accuracy of \sys{} Versus LRC-BQ.]{
    \label{fig:10-a}
    \includegraphics[width=0.355\textwidth]{figures/precision-1.eps}}
  \hspace{0.5in}
   \subfigure[Accuracy of Using Various Data Items for Modeling of \sys{}.]{
    \label{fig:11-a}
  \includegraphics[width=0.45\textwidth]{figures/precisionofdifferentfeatures.eps}}
  \caption{Performance of \sys{} }
  \label{fig:fig-2}
  \vspace{-4ex}
\end{figure*}

@@

Fig.\ \ref{fig:11-a} explores the performance of \sys{} when using alternative data items for modeling.
By default, \sys{} uses ``UI+II+MI'', i.e., items of users (UI), microblogs (MI) and interactions (II).
How about using other combinations of the above item(s)?
As shown in Fig.\ \ref{fig:11-a}, the default setting wins in most cases.

@@

\begin{figure*}
  \centering
  \subfigure[]{
      \label{fig:userFeatures:uf-1}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/1.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-2}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/2.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-3}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/3.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-4}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/4.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-5}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/5.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-6}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/6.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-7}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/7.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-8}
      \includegraphics[width=0.24\textwidth]{IMAGE/features/userFeatures/8.eps}}
  \caption{Visualization for User Features.}
  \label{fig:userFeatures} %% label for entire figure
  \vspace{-4ex}
\end{figure*}

@@

\textbf{Summary}. From these experimental results we find the followings.
(1) We design a novel method to extract users' explicit/implicit interests. And we tested various $\alpha$ to get a good performance. The visualization for a typical user shows that our method can make sense.
(2) In this paper, we offer a clustering method K-Gru to deal with complex vectors. And it helps us find a reasonable clustering result.
(3) By modeling user behaviors over groups instead of a single model for all users as LRC-BQ, we improve the average accuracy over LRC-BQ by 6\%. What deserves to be mentioned is that the performance of LRC-BQ also improved a lot by user clustering.

### 2018-02-24 DASFAA18_CR/Gruba_final/10-appendix.tex

\section*{Appendix: Extra Experiments}
\label{sec:appendix}

%\subsection{Case Study for Feature Extraction}
\begin{figure*}
  \centering
  \subfigure[]{
  \label{fig:subfig1:fig11}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/11.eps}}
  \subfigure[]{
  \label{fig:subfig1:fig12}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/12.eps}}
  \subfigure[]{
  \label{fig:subfig1:fig13}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/13.eps}}
  \subfigure[]{
  \label{fig:subfig1:fig14}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/14.eps}}
  \subfigure[]{
  \label{fig:subfig1:fig15}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/15.eps}}
  \subfigure[]{
  \label{fig:subfig1:fig16}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/16.eps}}
  \subfigure[]{
  \label{fig:subfig1:fig17}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/17.eps}}
  \subfigure[]{
  \label{fig:subfig1:fig18}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/18.eps}}
  \subfigure[]{
  \label{fig:subfig1:fig19}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/19.eps}}
  \caption{The Statistics of User Group One}
  \label{fig:subfig1} %% label for entire figure
\end{figure*}

\subsection*{Exp-5: Case Study for User Clustering}

@@

>>>>

%\section*{Appendix: Extra Experiments}
%\label{sec:appendix}

%\subsection{Case Study for Feature Extraction}

\begin{figure*}
  \centering
  \subfigure[]{
  \label{fig:subfig1:fig11}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/11.eps}}
  \subfigure[]{
  \label{fig:subfig1:fig12}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/12.eps}}
  \subfigure[]{
  \label{fig:subfig1:fig13}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/13.eps}}
  \subfigure[]{
  \label{fig:subfig1:fig14}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/14.eps}}
  \subfigure[]{
  \label{fig:subfig1:fig15}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/15.eps}}
  \subfigure[]{
  \label{fig:subfig1:fig16}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/16.eps}}
  \subfigure[]{
  \label{fig:subfig1:fig17}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/17.eps}}
  \subfigure[]{
  \label{fig:subfig1:fig18}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/18.eps}}
  \subfigure[]{
  \label{fig:subfig1:fig19}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/19.eps}}
  \caption{The Statistics of User Group One}
  \label{fig:subfig1} %% label for entire figure
\end{figure*}
\subsection*{Exp-5: Case Study for User Clustering}

@@

\begin{table}[tb!]
\centering
\begin{small}
\caption{Variables}
\vspace{0.1cm}
\label{tbl:Variables1}
\begin{tabular}{lll}
\toprule
\multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}}	& \multicolumn{1}{l}{\textbf{Section}} \\	\midrule \midrule
$M_b$             & a microblog     	  &2			\\	\midrule
$O$               & owner of a microblog           	  &2			\\	\midrule
$T$               & the generated time of a microblog	  &2			\\	\midrule
$M$               & the message context of a microblog	  &2			\\	\midrule
$flag$            & flag denoting $M_b$ is retweeted (1) or originally tweet (0) by O	  &2			\\	\midrule
$u$               & user $u$	  &2			\\	\midrule
$B_u$             & microblogs of user $u$	  &2			\\	\midrule
$R_u$             & followers of user $u$	  &2			\\	\midrule
$E_u$             & followees of user $u$	  &2			\\	\midrule
$\mathbb{U}$      & a set of users	  &2			\\	\midrule
$\mathbb{B}$      & a set of microblogs	  &2			\\	\midrule
$b$               & a microblog	  &2			\\	\midrule
$f$               & a follower	  &2			\\	\midrule
$G_u$				& gender of user $u$		        &3       		\\	\midrule
$P_u$				& province of user $u$				&3              \\	\midrule
                    & a ratio defined as the number     &         \\	
                    & of followers over that of         &3         \\		
\raisebox{1.5ex}{$R_{ee,u}$}  &followees,i.e.,$\frac{\#R_u}{\#E_u}$       &      \\  \midrule
$U_{t,u}$		    & user type (as illustrated in Table \ref{tbl:ucate}) &3        \\ \midrule	
$R_{oc,u}$          & ratio that is the number of retweeted microblogs over that of originally tweeted	  &3			\\	\midrule
$W_{r,u}$           & average number of retweeted microblogs per week	  &3			\\	\midrule
$W_{t,u}$           & average number of tweeted microblogs per week	  &3			\\	\midrule
$P_{rt,u}$          & normalized vector regarding the time distribution of a user’s retweeting  behavior	  &3			\\	\midrule
$P_{tt,u}$          & normalized vector regarding the time distribution of a user’s tweeting  behavior	  &3			\\	\midrule
$P_{rg,u}$          & normalized vector with respect to the gap distribution of a user’s retweeting behavior	  &3			\\	\midrule
$P_{tg,u}$          & normalized vector with respect to the gap distribution of a user’s tweeting behavior	  &3			\\	\midrule
$L$                 & A lexicon consists of a set of topics	  &3			\\	\midrule
$t$                 & A topic in $L$	  &3			\\	\midrule
$c$                 & A cell word in $L$	  &3			\\	\midrule
$P_u$               & The interest feature of a user $u$	  &3			\\	\midrule
$WS$                & a word set	  &3			\\	\midrule
$W_f$               & a metric TF-IDF weight	  &3			\\	\midrule
$b_i$               & the occurrences of word $w_i$ in microblog $b$	  &3			\\	\midrule
$|D_i|$             & the number of microblogs which contains word $w_i$	  &3			\\	\midrule
$|D|$               & the number of all microblogs	  &3			\\	\midrule
$N_t$               & the number of words in topic $t$	  &3			\\	\midrule
$W_w$               & A metric Twitter-LDA weight	  &3			\\ \bottomrule
\end{tabular}
\end{small}
\end{table}

\begin{table}[tb!]
\centering
\begin{small}
\caption{Variables}
\vspace{0.1cm}
\label{tbl:Variables2}
\begin{tabular}{lll}
\toprule
\multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}}	& \multicolumn{1}{l}{\textbf{Section}} \\	\midrule \midrule
$\alpha$            & a parameter set flexible priorities between TF-IDF and Twitter-LDA	  &3			\\	\midrule
$t_k$               & a topic in $L$	  &3			\\	\midrule
$b_m$               & a microblog of user $u$	  &3			\\	\midrule
$B_s(u)$            & microblogs of user $u$	  &3			\\	\midrule
$s_k$               & overall similarity of user $u$ over topic $t_k$	  &3			\\	\midrule

$Y'$,$Z'$           & numerical vectors	  &4			\\	\midrule
$Y''$,$Z''$          & categorical vectors	  &4			\\	\midrule
$Y^{\ast}$,$Z^{\ast}$     & vectors where each dimension is a normalized vector per se	  &4			\\	\midrule
$d_i(u)$            & the average distance to all the other users in the same cluster	  &4			\\	\midrule
$d_o(u)$            & the minimum of the distances between $u$ and other clusters	  &4			\\	\midrule
$v(u)$              & The Silhouette coefficient value	  &4			\\	\midrule

$E$                 & An item $E$ involves a microblog $b$ and a user $f$ such that $f\ \in R_{b.O}$	  &5			\\	\midrule
$C_h$               & the correlation metric $C_h$ of $b$ and event	  &5			\\	\midrule
$W_s$               & $u$'s short-term interest	  &5			\\ \bottomrule
\end{tabular}
\end{small}
\end{table}

\begin{table}[tb!]
\centering
\begin{small}
\caption{Variables}
\vspace{0.1cm}
\label{tbl:Variables2}
\begin{tabular}{ll|ll}
\toprule
\multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}}
& \multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}} \\	\midrule \midrule
$L$                 & A lexicon consists of a set of topics	
&$t$                 & A topic in $L$	 			\\	\midrule
$c$                 & A cell word in $L$	
&$P_u$               & The interest feature of a user $u$	 			\\	\midrule
$WS$                & a word set	 			
&$W_f$               & a metric TF-IDF weight				\\	\midrule
$b_i$               & the occurrences of word $w_i$ in microblog $b$	
&$|D_i|$             & the number of microblogs which contains word $w_i$			\\	\midrule
$|D|$               & the number of all microblogs
&$N_t$               & the number of words in topic $t$				\\	\midrule
$W_w$               & A metric Twitter-LDA weight
&$\alpha$            & a parameter set flexible priorities between TF-IDF and Twitter-LDA			\\	\midrule
$t_k$               & a topic in $L$	
&$b_m$               & a microblog of user $u$			\\	\midrule
$B_s(u)$            & microblogs of user $u$	
&$s_k$               & overall similarity of user $u$ over topic $t_k$			\\	\bottomrule
\end{tabular}
\end{small}
\end{table}

\begin{table}[]
\centering
\caption{My caption}
\label{my-label}
\begin{tabular}{|l|l|l|l|}
\hline
\alpha & accuracy & precision & recall &  \\ \hline
0	&0.488500	&0.636667	&0.560833     \\ \hline
0.1	&0.479167	&0.633333	&0.557500     \\ \hline
0.2	&0.481333	&0.636667	&0.564167     \\ \hline
0.3	&0.506500	&0.663333	&0.588333     \\ \hline
0.4	&0.497167	&0.660000	&0.587500     \\ \hline
0.5	&0.497583	&0.666667	&0.600833     \\ \hline
0.6	&0.524417	&0.693333	&0.622500     \\ \hline
0.7	&0.576583	&0.720000	&0.649167     \\ \hline
0.8	&0.502250	&0.650000	&0.590833     \\ \hline
0.9	&0.450583	&0.596667	&0.550833     \\ \hline
1	&0.396417	&0.536667	&0.501667     \\ \hline
\end{tabular}
\end{table}
